%-------------------------
% CV in Latex
% Adapted from a resume template provided by the user
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\usepackage[T1]{fontenc}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\renewcommand*\familydefault{\sfdefault}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey} #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

\begin{document}

\begin{center}
    \textbf{\Huge Xu Hu} \\ \vspace{5pt}
    \small Former Senior Undergraduate @ AHU / Visiting Student @ NCSU \\
    \small Ph.D. Student @ UT Dallas \\ \vspace{4pt}
    \small \faEnvelope \hspace{2pt} \texttt{\href{mailto:xu.hu@utdallas.edu}{xu.hu@utdallas.edu} / \href{mailto:huxu896@gmail.com}{huxu896@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faGraduationCap \hspace{2pt} \href{https://scholar.google.com/citations?user=4LvTffEAAAAJ&hl=en}{\myuline{Google Scholar}} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Richardson, TX, USA}
    \\ \vspace{-3pt}
\end{center}

\section{EDUCATION BACKGROUND}
  \resumeSubHeadingListStart

    \resumeSubheading
      {The University of Texas at Dallas, Texas, U.S.A.}{2025 -- 2030 (expected)}
      {Ph.D. Student, Department of Computer Science}{Richardson, TX, USA}
      \resumeItemListStart
        \resumeItem{Advisors: Associate Professor Feng Chen and Assistant Professor Bingze Li}
        \resumeItem{Research Interests: large language model hallucination, trustworthiness, and agents}
      \resumeItemListEnd

    \resumeSubheading
      {Anhui University (Project ``211''), Hefei, China}{2021 -- 2025}
      {B.E. in Economic Statistics, Department of Big Data and Statistics}{Hefei, China}
      \resumeItemListStart
        \resumeItem{Overall GPA: 4.16/5.00; Major GPA: 4.33/5.00; WES: 3.92/4.00; Major Rank: 1/103 (Top 0.95\%)}
        \resumeItem{Main Courses: Mathematical Analysis I \& II (90, 94), Advanced Algebra (87), Probability and Mathematical Statistics (89), Operations Research (97), Statistics (94), Bayesian Statistics (100), R Programming (95), Python Programming (95), Data Mining (93), Applied Statistical Analysis (95), Statistical Forecasting and Decision (96), Intermediate Econometrics (96), Time Series (91)}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{PUBLICATIONS}
  \begin{enumerate}[leftmargin=0.22in, itemsep=2pt, topsep=2pt]
    \small
    \item Hu Xu, Yu Jianwen, Xu Qin, Tao Zhifu, ``Volatility information in high-frequency financial interval-valued time series: A direct modeling pattern,'' \textit{Fluctuation and Noise Letters}, 2024. SCI.
    \item ``Application of a Latent Diffusion Model for MRI Generation: Integrating 3D Autoencoder with KL Divergence Loss and a ViT-based Denoising Framework,'' \textit{IEEE ISBI 2025}, first author.
  \end{enumerate}

\section{RESEARCH EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ISE, Edward P. Fitts Department, North Carolina State University}{Aug. 2024 -- Nov. 2024}
      {Student Intern, under the supervision of Prof. Xiaolei Fang and Prof. Shu-Cherng Fang}{Raleigh, NC, USA}

      \resumeProjectHeading
        {\textbf{Adaptive Diffusion Models for Industrial Irregular Time Series Analysis}}{}
        \resumeItemListStart
          \resumeItem{Applied conditional diffusion models to sparse, irregular, and missing time-series data in industrial settings.}
          \resumeItem{Implemented domain adaptation by replacing Gaussian noise with Brownian motion-based noise to match real-world sensor data characteristics.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Path-Aware Wiener Process Framework for RUL Prediction}}{}
        \resumeItemListStart
          \resumeItem{Developed a novel deep learning framework combining an attention mechanism with a Wiener process for multi-condition remaining useful life prediction.}
          \resumeItem{Designed a path-aware embedding module to capture operating-condition transitions and duration effects through an attention mechanism.}
          \resumeItem{Implemented variational inference to model unit-to-unit degradation patterns and mutual information-based sensor attention.}
        \resumeItemListEnd

    \resumeSubheading
      {Data Science and Analytics Thrust, HKUST Guangzhou}{Jun. 2024 -- Aug. 2024}
      {Research Intern, under the supervision of Prof. Yuxuan Liang and Prof. Zhengyang Zhou}{Guangzhou, China}

      \resumeProjectHeading
        {\textbf{Spatio-Temporal Selective State Space (ST-Mamba) Model for Traffic Flow Prediction}}{}
        \resumeItemListStart
          \resumeItem{Developed a spatio-temporal model without explicit graph modeling.}
          \resumeItem{Effectively captured long-range dependencies in traffic flow data.}
          \resumeItem{Employed the Mamba block to improve computational efficiency and prediction accuracy.}
          \resumeItem{Conducted ablation studies and derived new observations about state space models.}
        \resumeItemListEnd

    \resumeSubheading
      {TReNDS Lab, ECE, GSU / Georgia Tech / Emory}{Jun. 2024 -- Aug. 2024}
      {Collaborated with Ph.D. student Yuda Bi; under the supervision of Prof. Vince D. Calhoun}{Atlanta, GA, USA}

      \resumeProjectHeading
        {\textbf{Functional-to-Structural MRI Image Translation based on Conditional Latent Diffusion: Biomarker Identification for Schizophrenia}}{}
        \resumeItemListStart
          \resumeItem{Utilized an improved Diffusion Transformer (DiT) to achieve reverse generation from functional network connectivity (FNC) to gray matter (GM).}
          \resumeItem{Introduced the FNC matrix as a condition in the DiT model to guide the GM generation process.}
          \resumeItem{Explored subject-specific biomarkers for schizophrenia using both functional and structural MRI data.}
        \resumeItemListEnd

    \resumeSubheading
      {Department of Big Data and Statistics, Anhui University}{Mar. 2023 -- Sep. 2023}
      {Undergraduate Research Project, under the supervision of Prof. Zhifu Tao}{Hefei, China}

      \resumeProjectHeading
        {\textbf{Volatility Information in High-Frequency Financial Interval-Valued Time Series: A Direct Modeling Pattern}}{}
        \resumeItemListStart
          \resumeItem{Developed a novel VAR-NN forecasting model combining a vector autoregressive process, volatility information, and neural networks.}
          \resumeItem{Introduced four types of interval-valued data volatility information for more accurate predictions.}
          \resumeItem{Outperformed traditional methods in forecasting high-frequency financial data.}
        \resumeItemListEnd

    \resumeSubheading
      {College of Computing and Data Science, NTU Singapore}{Jul. 2023 -- Aug. 2023}
      {AI Summer School; Best Project Award; Excellence Leadership Award}{Singapore}

      \resumeProjectHeading
        {\textbf{Location-based Demand Prediction and Resource Optimization System for California Bike-sharing}}{}
        \resumeItemListStart
          \resumeItem{Built a system for real-time prediction and optimization of dynamic demand in bike-sharing systems.}
          \resumeItem{Improved resource allocation efficiency and enhanced user experience.}
          \resumeItem{Supported smart urban transportation management with multidimensional data-driven decision-making.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{COMPETITION AWARDS}
  \resumeSubHeadingListStart

    \resumeSubheading
      {2023 ICM -- American Undergraduate Mathematical Modeling Competition, Finalist}{Feb. 2023}
      {Proposed a solution on network science and operations research}{Global Grand Prize Nomination (top 0.17\%)}
      \resumeItemListStart
        \resumeItem{Applied canonical correlation analysis to the United Nations' 17 Sustainable Development Goals.}
        \resumeItem{Used advanced econometric methods to analyze factors influencing progress.}
        \resumeItem{Utilized an LSTM to predict achievable goals over the next decade.}
        \resumeItem{Concluded with a sensitivity analysis, affirming the robustness of the model.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{HONORARY \& LEADERSHIP}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
      \textbf{Student Assistant of the President, Anhui University} \hfill {\color{dark-grey} Jun. 2022 -- Jun. 2023} \\
      The first junior undergraduate selected.
    }}
    \small{\item{
      \textbf{Honors} : Outstanding Student Award, Academic Excellence Award, etc.
    }}
    \small{\item{
      \textbf{Membership} : SWE - Society of Women Engineers
    }}
 \end{itemize}

\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Professional Qualification} : ACCA (2022): Passed BA, MA, FA; BEC Medium \vspace{2pt} \\
     \textbf{Computer Skills} : Python, R, PyTorch, LaTeX
    }}
 \end{itemize}

\end{document}
